---
title: "W_UP_01"
author: "steven"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

The question is there a difference between the average number of pushups that can be done in 2 minutes between football players who play on the line compared to players that are skilled.
The data came from George town college in Kentucky.

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

is there a difference between average number of pushups that can be done by line vs skills?

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

Pushups is a numerical variable, position is a categorical.Therefore we use numerical-cat file.

# Results

The graph indicates the skilled players completed more push-ups comapred to the line players. 

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results



### Graphical Descriptive Results

```{r}
boxplot(pushups~position, data=mydata)
```
This box plot shows that the skilled players completed more pushups in 2 minutes, on average to the line players.


```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The plot shows that the skill players completed more pushups compared to the line players. the middle for the line gys was 15 and the middle for the skill players was 50

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups ~ position, data=mydata)
```

The table shows that the average number of push-ups for a line player was about 17 while the average for a skilled player was 50. 

## Inferential Results

```{r}
t.test(pushups~position, data=mydata)
```
The P value is less than o.o5, so we reject the null hypothesis and we conclude that there is a difference between the average number of pushups between line players and skilled players.

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->




# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was is there a difference in the average number of push-ups that skilled and line players can do in a 2 minute time period. Yes, there is a difference with the P value. 

